---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# modeltools

<!-- badges: start -->
[![R-CMD-check](https://github.com/edsandorf/modeltools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/edsandorf/modeltools/actions/workflows/R-CMD-check.yaml)
[![Coverage Status](https://codecov.io/github/edsandorf/modeltools/coverage.svg?branch=main)](https://app.codecov.io/github/edsandorf/modeltools?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of modeltools is to provide small, reusable tools for econometric modeling in R, with a particular focus on choice models estimated with [bgw](https://CRAN.R-project.org/package=bgw). Model objects work with the `stats`, `broom` and `sandwich` generics, so standard tools such as `AIC()`, `tidy()` and `sandwich()` work out of the box.

## Installation

You can install the development version of modeltools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edsandorf/modeltools")
```

## Example

Robust standard errors for a model estimated with `bgw_mle()`:

```{r bgw-example, eval = FALSE}
library(modeltools)

model <- bgw::bgw_mle(
  log_lik, 
  betaStart = beta, 
  bgw_settings = list(vcHessianMethod = "finiteDifferences")
)
model <- add_scores(model, log_lik)

tidy(model, vcov = sandwich(model))
prep_for_gt(model, vcov = vcovCL(model, cluster = db$id))
```

Comparing two empirical distributions using the Poe et al. (2005) test:

```{r poe-example, message = FALSE}
library(modeltools)

set.seed(123)
wtp_a <- rnorm(1000, mean = 0.5)
wtp_b <- rnorm(1000, mean = 1)
poe_test(wtp_a, wtp_b)
```
